Fractal modelling

### 2012-07-08 fractal paper/src/fractal.tex
...

The earliest examples of fractals were described around the beginning of the twentieth century as counterexamples to conjectures in planar geometry and largely considered pathological. It was not until the 1970s that they were considered as a family of mathematical objects that could accurately describe many physical phenomena. Coast lines, trees, clouds and lightning bolts could all be described more accurately as fractals, than as lines, spheres or cubes.

@@

So far, two approaches have succesfully tackled the inverse problem in some form:
\begin{itemize}
  \item Genetic algorithms. A straightforward search through the space of IFSs. The drawback of this approach is one of time complexity. The running time of these approaches scale poorly in the number of dimensions and components.
  \item Partitioned iterated function systems. This is a modified version of the problem to make the model tractable and feaible in the domina of image compression. This approach does not translate well to n-dimensional point patterns.
\end{itemize}

>>>>

The earliest examples of fractals were described around the beginning of the twentieth century as counterexamples to conjectures in planar geometry and mostly considered pathological. It was not until the 1970s that they were began to be seen as a single and useful family of mathematical objects that could accurately describe many physical phenomena. Coast lines, trees, clouds and lightning bolts can all be described more accurately as fractals than as lines, spheres or cubes.

@@

So far, two approaches have succesfully tackled the inverse problem in some form:
\begin{itemize}
  \item Genetic algorithms!@. A straightforward search through the space of IFSs. The drawback of this approach is one of time complexity. The running time of these approaches scale poorly in the number of dimensions and components.
  \item Partitioned iterated function systems!@. This is a modified version of the problem to make the model tractable and feasible in the domain of image compression. This approach does not translate well to n-dimensional point patterns.
\end{itemize}
